---
title: "Basic R exercise"
author:   "Yuxin_Shuai"
output: html_notebook
---

## Basic 20 Questions

1. Data construction

```{r}
## sol_1
df <- data.frame(
  "grammer"=c("Python","C","Java","GO",NA,"SQL","PHP","Python"),
  "Score"=c(1,2,NA,4,5,6,7,10)
)
df
```
```{r}
## sol_2
library(tibble)
df <- tibble(
  "grammer"=c("Python","C","Java","GO",NA,"SQL","PHP","Python"),
  "Score"=c(1,2,NA,4,5,6,7,10)
)
df

```

2. Extract the row which contains "Python"



```{r}
df[which(df$grammer=="Python"),]
```
3. Export all the column names of df

```{r}
names(df)
```
4. Alter the name of second column to "Popularity"
```{r}
options(warn=-1)
library(dplyr)
library(tidyverse)
df <- df %>% rename(popularity = Score)
```
```{r}
df
```
5. Calculate the frequency of each programming language in column "grammer"
```{r}
table(df$grammer)
```
6. Replace NA with average of popularity

```{r}
library(Hmisc)
df$popularity <- impute(df$popularity,mean)
```
```{r}
df
```
7. Extract the row where its value is greater than 3 in column "popularity"

```{r}
df %>% filter(popularity >3)
```

8. Duplicate removal of column grammer

```{r}
df[!duplicated(df$grammer),]
```

