---
title: "Basic R exercise"
author:   "Yuxin_Shuai"
output: html_notebook
---

>__Basic 20 Questions__

1. Data construction

```{r}
## sol_1
df <- data.frame(
  "grammer"=c("Python","C","Java","GO",NA,"SQL","PHP","Python"),
  "Score"=c(1,2,NA,4,5,6,7,10)
)
df
```
```{r}
## sol_2
library(tibble)
df <- tibble(
  "grammer"=c("Python","C","Java","GO",NA,"SQL","PHP","Python"),
  "Score"=c(1,2,NA,4,5,6,7,10)
)
df

```

2. Extract the row which contains "Python"



```{r}
df[which(df$grammer=="Python"),]
```
3. Export all the column names of df

```{r}
names(df)
```
4. Alter the name of second column to "popularity"
```{r}
options(warn=-1)
library(dplyr)
library(tidyverse)
df <- df %>% rename(popularity = Score)
```
```{r}
df
```
5. Calculate the frequency of each programming language in column "grammer"
```{r}
table(df$grammer)
```
6. Replace NA with average of popularity

```{r}
library(Hmisc)
df$popularity <- impute(df$popularity,mean)
```
```{r}
df
```
7. Extract the row where its value is greater than 3 in column "popularity"

```{r}
df %>% filter(popularity >3)
```

8. Duplicate removal of column grammer

```{r}
df[!duplicated(df$grammer),]
```

9. Calculate the mean of column popularity

```{r}
mean(df$popularity)
```

```{r}
df %>%
  summarise(mean = mean(popularity))
```

10. Convert grammer to list

```{r}
unlist(df$grammer)
```

11. Export DataFrame to Excel

```{r}
library(readr)
write_excel_csv(df,'filename.csv')
```

12. Search for the dimension of DataFrame

```{r}
dim(df)
```
13. Extract the row where the value of popularity is larger than 3 and smaller than 7

```{r}
df %>% filter(popularity >3 & popularity <7)
```

14. swap the columns popularity and grammer

```{r}
df <- df %>%
    select(popularity,everything())
```
```{r}
df
```

15. Extract the row where its value is largest in column popularity

```{r}
df %>% filter(popularity == max(popularity))
```

16. Extract the last five rows

```{r}
tail(df,5)
```

17. Delete the last row

```{r}
df[-dim(df)[1],]
```

18.Add row ['perl',6.6]

```{r}
row <- data.frame(
  "grammer" = c("Perl"),
  "popularity" = c(6.6)
)
df <- rbind(df,row)
```
 
19. Sort dataframe from small to big

```{r}
df<- df%>% arrange(popularity)
```

20. Calculate the length of string

```{r}
library(Hmisc)
library(stringr)
df$grammer <- impute(df$grammer,'R')
str_length(df$grammer)

df$len_str <- str_length(df$grammer)
```

21. Read excel

```{r}
df <- read_csv('pandas120.csv')
```













































